EUC_PVE

### 2014-07-24 markdowns/master.rmd
split photochem script into just model analysis and then predict plots with bins for master
added photochem predict to master and md

added new lables to plot objects

```
seedling growth through time
```
```{r allometry panel plot}
source("master_scripts/allometryplotting.R")
```

```
seedling total leaf area through time
```
```{r leaf area plot}
source("master_scripts/leafarea_plotting.R")
```

```
root:shoot and leaf:fine root at harvest
```

@@

```
aci curves and jmax/vcmax
```

@@

```
Soil N percent pre expeeriment and at harvest
```
```{r Soil N percent}
source("master_scripts/soilN_plotting.R")
```

>>>>

seedling growth through time

```{r allometry panel plot}
source("master_scripts/allometryplotting.R")
```

seedling total leaf area through time

```{r leaf area plot}
source("master_scripts/leafarea_plotting.R")
```

root:shoot and leaf:fine root at harvest

@@

aci curves and jmax/vcmax

@@

Soil N percent pre expeeriment and at harvest

```{r Soil N percent}
source("master_scripts/soilN_plotting.R")
```

Predicted responses of Amax on a mass basis to leaf starch and N levels
```{r Amass vs TNC and N}
source(("master_scripts/photochem_predict.R")
```
